---
title: "Reproductive Health Behaviors in Developing Countries"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rio)
library(here)
library(tidyverse)
library(ggplot2)
library(ggtext)
library(janitor)
project_data<-import(here("data","Final_project_data.csv"))%>%
  clean_names()

```

Page 1
===================================== 
    
Column {data-width=650}
-----------------------------------------------------------------------

### Line Chart

```{r}
project_data%>%
  ggplot(aes(x=year))+
  geom_point(aes(x=year, y = br_pak),color="green",size=1,shape=16)+
  geom_line(aes(y=br_pak),color="green")+
  geom_point(aes(x=year, y = br2),color="blue",size=1,shape=18)+
  geom_line(aes(y=br2),color="blue")+
  geom_point(aes(x=year, y = br3),color="orange",size=1,shape=17)+
  geom_line(aes(y=br3),color="orange")+
  theme_minimal()+
  scale_x_continuous(breaks = seq(1961,2022,by=5),
                     labels = seq(1961,2022,by=5),
                     expand = c(0,0),
                     limits = c(1961,2022))+
  labs("x=Year",
       y="Birth Rates by Country",
       title="Decreasing birthrates in South Asia",
      caption="Data from World Bank") +
  annotate(
    'text',
    x = 1966,
    y = 45,
    label = 'Pakistan',
    size = 3
  )+
annotate(
    'text',
    x = 1966,
    y = 50,
    label = 'Bangladesh',
    size = 3
  )+
annotate(
    'text',
    x = 1966,
    y = 42,
    label = 'India',
    size = 3
  )
```
    
Column {data-width=350}
-----------------------------------------------------------------------

### About 
This line chart shows how GDP of the three countries including Pakistan, India and Bangladesh is related to the birth rate.

### Original 


Page 2
===================================== 
    
Column {data-width=650}
-----------------------------------------------------------------------


```{r}
### Scatter Plots - Pakistan & India
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br_pak,y=gdp_pak, size = women_political_pak)) +
  geom_point(alpha = .5)+
  theme_minimal()
```


```{r}
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br2,y=gdp_ind, size = women_india)) +
  geom_point(alpha = .5)+
  theme_minimal()
```

Column {data-width=350}
-----------------------------------------------------------------------

### About 
The three scatterplots show how the indicators of women empowerment in each country including Pakistan, India, and Bangladesh impact birth rate. The variable "women's_political_participation is used as the indicator of women empowerment. 


### Original 

```{r}
```

Page 3
===================================== 
    
Column {data-width=650}
-----------------------------------------------------------------------

### Scatter Plot - Bangladesh

```{r}
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br3,y=gdp_bangladesh, size = women_bangladesh)) +
  geom_point(alpha = .5)+
  theme_minimal()
```

Column {data-width=350}
-----------------------------------------------------------------------

### About 
In conclusion, this study aims to bridge the gap in literature by employing an extensive analysis of World Bank demographic data to explore the interconnections between GDP, birth rates, and women’s political participation in Pakistan, India, and Bangladesh. Through exploratory data analysis and innovative visualizations, the research intends to provide policymakers, public health officials, NGOs, and the academic community with actionable insights to refine and enhance family planning initiatives, considering the unique demographic and cultural contexts of South Asia.



### Original 

```{r}
```
