---
title: "Reproductive Health Behaviors in Developing Countries"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rio)
library(here)
library(tidyverse)
library(ggplot2)
library(ggtext)
library(janitor)
project_data<-import(here("data","Final_project_data.csv"))%>%
  clean_names()

```

Page 1
===================================== 
    
Column {data-width=650}
-----------------------------------------------------------------------

### Line Chart

```{r}
project_data%>%
  ggplot(aes(x=year))+
  geom_point(aes(x=year, y = br_pak),color="green",size=1,shape=16)+
  geom_line(aes(y=br_pak),color="green")+
  geom_point(aes(x=year, y = br2),color="blue",size=1,shape=18)+
  geom_line(aes(y=br2),color="blue")+
  geom_point(aes(x=year, y = br3),color="orange",size=1,shape=17)+
  geom_line(aes(y=br3),color="orange")+
  theme_minimal()+
  scale_x_continuous(breaks = seq(1961,2022,by=5),
                     labels = seq(1961,2022,by=5),
                     expand = c(0,0),
                     limits = c(1961,2022))+
  labs("x=Year",
       y="Birth Rates by Country",
       title="Decreasing birthrates in South Asia",
      caption="Data from World Bank") +
  annotate(
    'text',
    x = 1966,
    y = 45,
    label = 'Pakistan',
    size = 3
  )+
annotate(
    'text',
    x = 1966,
    y = 50,
    label = 'Bangladesh',
    size = 3
  )+
annotate(
    'text',
    x = 1966,
    y = 42,
    label = 'India',
    size = 3
  )
```

Column {data-width=350}
-----------------------------------------------------------------------

### About 

```{r}
# 1 Comparative Line Chart
Comparative line charts illustrate the trends in GDP rates and birth rate contributing to the overall population growth over time, providing a clear visual comparison across the three countries over last six decades.


Page 2
===================================== 
    
Column {data-width=650}
-----------------------------------------------------------------------

### Line Chart

```{r}
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br_pak,y=gdp_pak, size = women_political_pak)) +
  geom_point(alpha = .5)+
  theme_minimal()+
labs("x=Year",
       y="Birth Rates by Country",
       title="Decreasing birthrates in South Asia",
      caption="Data from World Bank") 
```

### Chart C

```{r}
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br2,y=gdp_ind, size = women_india)) +
  geom_point(alpha = .5)+
  theme_minimal()
```

Page 3
===================================== 
    
Column {data-width=650}

### About 

```{r}
# 2 Scatter Plots

Moreover, scatter plots will be used to explore and present the relationships between women political participation and birth rates, highlighting potential correlations. The reason for choosing political participation is because it is an indicator of women empowerment in the given country, which in turns results in higher education and literacy about making own decisions, and access to various contraceptive methods.

Three scatter plots show how the three different South Asian countries, Pakistan, India, and Bangladesh’s GDP is connected with it’s women’s political participation. 

```


### Original 

```{r}
```
-----------------------------------------------------------------------

### Bubble Chart

```{r}
project_data%>%
  slice(37:62)%>%
  ggplot(aes(x=br3,y=gdp_bangladesh, size = women_bangladesh)) +
  geom_point(alpha = .5)+
  theme_minimal()
```

Column {data-width=350}
-----------------------------------------------------------------------

### About 

```{r}
# 2 Scatter Plots

Moreover, scatter plots will be used to explore and present the relationships between women political participation and birth rates, highlighting potential correlations. The reason for choosing political participation is because it is an indicator of women empowerment in the given country, which in turns results in higher education and literacy about making own decisions, and access to various contraceptive methods.

Three scatter plots show how the three different South Asian countries, Pakistan, India, and Bangladesh’s GDP is connected with it’s women’s political participation. 

```


### Original 

```{r}
```
